Easy as Pi, Volume II: On the Goodput and Energy of Network Coding Schemes in the Raspberry Pi

### 2016-06-28 introduction.tex
Removing redundant sections
Some edits

Our work is organized as follows. Section~\ref{sec:testbed} introduces the
testbed system, its setup, files configuration, connectivity and compilation of
the Kodo library. Section~\ref{sec:schemes} defines the coding schemes employed
in our study. Later, in Section~\ref{sec:metrics} we describe the considered
metrics and methodology for performance comparison of the codes deployed in
the \ac{Raspi}. In Section~\ref{sec:measurements}, we show the measurements in
the \ac{Raspi} models of the mentioned metrics. Final conclusions and future work
are reviewed in Section~\ref{sec:conclusions}.

>>>>

Our work is organized as follows. Section~\ref{sec:schemes} defines the
coding schemes employed in our study. Later, in Section~\ref{sec:metrics}
we describe the considered metrics and methodology for performance comparison
of the codes deployed in the \ac{Raspi}. In Section~\ref{sec:measurements}, we
show the measurements in the \ac{Raspi} models of the mentioned metrics
providing full discussions about the observed operational regimes. Final
conclusions and future work are reviewed in Section~\ref{sec:conclusions}.

### 2016-06-28 schemes.tex
Some edits

The difference between $b$ and $g$ is equal to the losses in the channel and the
losses due to linear dependencies. Therefore, in a lossless channel, the budget
is
\begin{equation}\label{eq:budget}
    b(g,d)=\sum^{g-1}_{i=0}\frac{1}{P(i,g,d)},
\end{equation}
where $P(i,g,d)$ is the probability of receiving an innovative coded packet
after receiving $i$ \ac{l.i.} packets with a coding density $d$. In our implementations, we considered the the upper bound for the innovation probability from \cite{feizi2014tunable}, given as
\begin{equation}
    P(i,g,d)\geq 1-(1-d)^{g-i}
\end{equation}

@@

The transmissions made between feedback packets are called the density
regions since the same estimated density is used for encoding sparse
packets. Once a new feedback is received, an encoder recalculates the
coding density for the new region until the next feedback packet is
received. before the coding density can be estimated, it is essential
that the encoder has a good estimate of the decoder \ac{dof}, but also
the remainder of the total budget. To calculate the density, we use
bisection to estimate a fixed density for the density region that
satisfies the budget for the $k$-th density region:
\begin{equation}
b(s(k-1),r(k),g,d) = \sum^{r(k)}_{i=r(k-1)} \frac{1}{P(i,g,d)} = \sum^{r(k)}_{i=r(k-1)} \frac{1}{1-(1-d)^{g-i}} = \frac{b}{2^k}, k\in [1,...).
\end{equation}
%
% Where the budget is half of the remaining budget for all the density regions
% except the last one, to which it is assigned the remaining of the budget.
The feedback scheme based on the rank reports
of~\eqref{eq:feedback_dofs} roughly splits the remaining coding
regions in two halves. In other words, the first half is the region
where the encoder currently operates. Once an encoder finishes with
this region, it proceeds with second half where again it splits this
into to two region and so on until it finishes on transmitting the
whole generation. This is also the case for the budget that is split
equally among the two new regions. The very last region will be
assigned the full remainder of the total budget and the coding density
will not vary.

\subsection{Implementation for the Raspberry Pi Multicore Architecture}
\label{sub:implementation-multicore}

>>>>

The difference between $b$ and $g$ is equal to the losses in the channel
and the losses due to linear dependencies. Therefore, in a lossless
channel, the budget is:
\begin{equation}\label{eq:budget}
    b(g,d)=\sum^{g-1}_{i=0}\frac{1}{P(i,g,d)},
\end{equation}
where $P(i,g,d)$ is the probability of receiving an innovative coded packet
after receiving $i$ \ac{l.i.} packets with a coding density $d$. In our
implementations, we considered the lower bound for the innovation probability
from \cite{feizi2014tunable}, given as:
\begin{equation}
    P(i,g,d) \geq 1-(1-d)^{g-i}
\end{equation}

@@

The transmissions made between feedback packets are called the density
regions since the same estimated density is used for encoding sparse
packets. Once a new feedback is received, an encoder recalculates the
coding density for the new region until the next feedback packet is
received. before the coding density can be estimated, it is essential
that the encoder has a good estimate of the decoder \ac{dof}, but also
the remainder of the total budget. To calculate the density, we use
bisection to estimate a fixed density for the density region that
satisfies the budget for the $k$-th density region:
\begin{equation}
b(r(k),r(k+1),g,d) = \sum^{r(k+1)}_{i=r(k)} \frac{1}{P(i,g,d)} = \sum^{r(k+1)}_{i=r(k)} \frac{1}{1-(1-d)^{g-i}} = \frac{b}{2^k},\ k\in [1,\ldots)
\end{equation}
%
% Where the budget is half of the remaining budget for all the density regions
% except the last one, to which it is assigned the remaining of the budget.
The feedback scheme based on the rank reports
in~\eqref{eq:feedback_dofs} roughly splits the remaining coding
regions in two halves. In other words, the first half is the region
where the encoder currently operates. Once an encoder finishes with
this region, it proceeds with second half where again it splits this
into two new regions and so on, until it finishes the transmission the
whole generation. This is also the case for the budget that is split
equally among the two new regions. The very last region will be
assigned the full remainder of the total budget and the coding density
will not vary.

\subsection{Network Coding Implementation for the Raspberry Pi Multicore
Architecture}
\label{sub:implementation-multicore}
